%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Brad Bachu} is currently a PhD student at Princeton
University Department of Physics studying particle phenomenology.
He attained a BSc. in Physics and Mathematics from MIT in 2017 along 
with a minor in Philosophy. In 2012, he won the President's Gold Medal
and was the CXC top performer in Technical Studies.

\vspace{5pt}

\noindent\textbf{Arjun Isa Mohammed} a freshman at Waterloo University
(update as needed)
attained an open scholarship in Mathematics in 2016.
He was the top performer in Unit one Applied Mathematics.
Arjun has represented Trinidad twice at the International
Mathematics Olympiad, Thailand (2015) and Hong Kong (2016).
Arjun is currently pursuing Computer Engineering and Physics.
\vspace{5pt}

\noindent\textbf{Nicholas Sammy} was awarded the Dennis Irvine Award for 
the Most Outstanding Candidate Overall for CAPE 2010 from CXC. He took up 
his Open Scholarship at Imperial College London, graduating with a BSc in
Chemistry, having gained research experience into nanoparticulate catalysts 
for methane synthesis and homogeneous catalysts for hydrogenation of
biomass-derived compounds. Currently a researcher at UWI St Augustine,
his research area is in the field of heterogeneous catalysts for selective
oxidation of methane.

\vspace{5pt}

\noindent\textbf{Kerry Shastri Singh} won the President's Gold Medal in
2011. He was the CXC regional top performer in Mathematics and Natural
Sciences, as well as the winner of the Dennis Irvine award for the Most
Outstanding Candidate Overall. He also won Trinidad and Tobago's first
ever Silver Medal at the International Mathematical Olympiad in
Kazakhstan in 2010. Kerry graduated from MIT in 2016 with a major in
Biological Engineering and a minor in Theater Arts. He is currently a
Research Fellow in the Department of Genetics at Harvard Medical. In
his spare time, Kerry enjoys playing FIFA, going to the movies
and playing football.
