%------------------------------------------------------------------------------
% Author(s):
% Varaun Ramgoolie
% Copyright:
%  Copyright (C) 2020 Brad Bachu, Arjun Mohammed, Varaun Ramgoolie, Nicholas Sammy
%
%  This file is part of Applied-Mathematics-Unit2 and is distributed under the
%  terms of the MIT License. See the LICENSE file for details.
%
%  Description:
%     Year: 2011
%     Module: 2
%     Question: 4 
%------------------------------------------------------------------------------

%------------------------------------------------------------------------------
% 4 a
%------------------------------------------------------------------------------

\begin{subquestions}
	
\subquestion

We are given that accidents occur at an average rate of 3 per week on a particular stretch of road. We will let $X$ represent the amount of accidents which occur in one week. Thus, we can see that $X$ follows a Poisson distribution, given as,
\begin{equation}
	X \sim \text{Pois}(3) \,.
\end{equation}
	
\begin{subsubquestions}
	
\subsubquestion

We want to find $P(X=0)$. From \rdef{mod2:defn:Poisson}, we know that,
\begin{equation}
	P(X = x) =\frac{ 3 ^ x \times e^{-3}}{x!} \,. \label{2011:q4:Poisson1}
\end{equation}
	
Thus, we can calculate $P(X=0)$ as,
\begin{align}
	P(X=0) & = \frac{ 3 ^0 \times e^{-3}}{0!} \nn \\
	       & = \frac{ 1 \times e^{-3}}{1} \nn \\
	       & = \frac{1}{e^3} \,.
\end{align}
	
%------------------------------------------------------------------------------

\subsubquestion

We want to find $P(X > 3)$. Since the Poisson Distribution is discrete, we get that,
\begin{align}
	P(X>3) & =1-P(X \leq 3) \nn \\
	       & = 1 - [P(X=0)+P(X=1)+P(X=2)+P(X=3)] \,.
\end{align}

Using \req{2011:q4:Poisson1}, we can calculate $P(X>3)$ as follows,
\begin{align}
	P(X=0) & = \frac{1}{e^3} \,. \\ \nn \\
	P(X=1) & = \frac{ 3^1 \times e^{-3}}{1!} \nn \\
	       & = \frac{3 \times e^{-3}}{1} \nn \\
	       & = \frac{3}{e^3} \,. \\ \nn \\
	P(X=2) & = \frac{ 3^2 \times e^{-3}}{2!} \nn \\
	       & = \frac{9 \times e^{-3}}{2} \nn \\
	       & = \frac{9}{2e^3} \,. \\ \nn \\
	P(X=3) & = \frac{ 3^3 \times e^{-3}}{3!} \nn \\
	       & = \frac{27 \times e^{-3}}{6} \nn \\
	       & = \frac{27}{6e^3} \,. \\ \nn \\
	P(X>3) & =1-P(X \leq 3) \nn \\
		   & = 1 - [P(X=0)+P(X=1)+P(X=2)+P(X=3)] \nn \\
		   & = 1 - \left(\frac{1}{e^3} + \frac{3}{e^3} + \frac{9}{2e^3} + \frac{27}{6e^3} \right) \nn \\
		   & = 1 - \frac{13}{e^3} \nn \\
		   & = 0.353 \,.
\end{align}

%------------------------------------------------------------------------------

Given that there are 3 accidents in 1 week, there are therefore 6 accidents on average during a fortnight (2 week period). Thus, we will let $Y$ represent the number of accidents in a 2 week period. Since we know that $Y$ also follows a Poisson distribution, we can denote it as,
\begin{equation}
	Y \sim \text{Pois}(6) \,.
\end{equation} 

From \rdef{mod2:defn:Poisson}, we know that,
\begin{equation}
	P(Y = y) =\frac{ 6 ^ y \times e^{-6}}{y!} \,.
\end{equation}

Thus, we can find $P(Y=6)$ as follows,
\begin{align}
	P(Y = 6) & = \frac{ 6 ^ 6 \times e^{-6}}{6!} \nn \\	
	         & = \frac{46656 \times e^{-6}}{720} \nn \\
	         & = \frac{324}{5 \times e^6} \nn \\
	         & = 0.161 \,.
\end{align}

\end{subsubquestions}
	
%------------------------------------------------------------------------------
% 4 b
%------------------------------------------------------------------------------
	
\subquestion

It is given that the probability of a student passing the Statistics examination is $0.84$. If we let $X$ be the number of students that pass an examination, we can see that $X$ follows a Binomial distribution denoted as,
\begin{equation}
	X \sim \text{Bin}(0.84) \,.
\end{equation} 

From \rdef{mod2:defn:Binomial}, we know that,
\begin{equation}
	P(X = x) = { n \choose x} (0.84)^x (1-0.84)^{n-x} \,. \label{2011:q4:Bin1}
\end{equation}

In a group of 12 students, we want to find the probability that more than two thirds of the group passes the examination. That is, we want to find $P(X > 8)$. Since X is discrete, we know that,
\begin{equation}
	P(X > 8) = P(X=9)+P(X=10)+P(X=11)+P(X=12) \,.
\end{equation}

Using \req{2011:q4:Bin1}, we can calculate $P(X > 8)$ as follows,
\begin{align}
	P(X=9) & = { 12 \choose 9} \times (0.84)^9 \times (1-0.84)^{12-9} \nn \\
	       & = 220 \times (0.84^9) \times (0.16)^3 \nn \\
	       & = 0.188 \,. \\ \nn \\
	P(X=10) & = { 12 \choose 10} \times (0.84)^{10} \times (1-0.84)^{12-10} \nn \\
	        & = 66 \times (0.84)^{10} \times (0.16)^2 \nn \\
	        & = 0.296 \,. \\ \nn \\
	P(X=11) & = { 12 \choose 11} \times (0.84)^{11} \times (1-0.84)^{12-11} \nn \\
	        & = 12 \times (0.84)^{11} \times 0.16 \nn \\
	        & = 0.282 \,. \\ \nn \\
	P(X=12) & = { 12 \choose 12} \times (0.84)^{12} \times (1-0.84)^{12-12} \nn \\
	        & = 1 \times (0.84)^{12} \times 1 \nn \\
	        & = 0.123 \,. \\ \nn \\
	P(X > 8) & = P(X=9)+P(X=10)+P(X=11)+P(X=12) \nn \\
	         & = 0.188+0.296+0.282+0.123 \nn \\
	         & = 0.889 \,.        
\end{align}

%------------------------------------------------------------------------------
% 4 c
%------------------------------------------------------------------------------

\subquestion

In a box, there are 4 white marbles, 2 red marbles, and 3 black marbles. Three marbles are drawn from the 9 marbles without replacement.  

\begin{subsubquestions}
	
\subsubquestion

We want to find the probability that the marbles will be drawn in the order of white $\rightarrow$ black $\rightarrow$ red. The probability that the first marble drawn is white is $\frac{4}{9}$. The probability that the second marble drawn is black is $\frac{3}{8}$. The probability that the third marble drawn is red is $\frac{2}{7}$. Thus, from \rdef{mod2:defn:MultiplicationRule}, 
\begin{align}
	P(white \rightarrow black \rightarrow red) & = \frac{4}{9} \times \frac{3}{8} \times \frac{2}{7} \nn \\
	                                           & = \frac{1}{21} \,.
\end{align}
	
%------------------------------------------------------------------------------

\subsubquestion

We want to find the probability that one marble of each color will be chosen. We should notice that the probability obtained in \textbf{(c)(i)} is the same probability as any other arrangement of the colors. For example, due to the commutative property of multiplication, the probability of [white $\rightarrow$ black $\rightarrow$ red] would be the same probability of [red $\rightarrow$ white $\rightarrow$ black]. Thus, in order to find the probability that one marble of each color will be chosen, we can multiply $P(white \rightarrow black \rightarrow red)$ by the number of permutations of the colors White, Red and Black. From \req{mod2:defn:PermutationEqn}, we can find the number of permutations of 3 colors as follows,
\begin{align}
	^3P_3 & = \frac{3!}{(3-3)!} \nn \\
	      & = \frac{3!}{1} \nn \\
	      & = 6 \,.
\end{align}

Thus, the probability that one marble of each color will be chosen is,
\begin{align}
	P(\text{one of each color}) & = P(white \rightarrow black \rightarrow red) \times 6 \nn \\
	                     & = \frac{1}{21} \times 6 \nn \\
	                     & = \frac{2}{7} \,.
\end{align}

%------------------------------------------------------------------------------

\subsubquestion

We want to find the probability that the 3rd marble is white. In order to do this, we will split the marbles into 2 groups: White marbles (W) and not White marbles (W'). In the setup, there are 4 W marbles and 5 W' marbles. The different combinations of the 3 marbles chosen, with white being the last marble, are (W,W,W), (W'W,W), (W,W',W) and (W', W',W). Thus, we find the probability that the 3rd marble is white by summing the probabilities of the different combinations as follows,
\begin{align}
	P(W,W,W) & = \frac{4}{9} \times \frac{3}{8} \times \frac{2}{7} \nn \\
	         & = \frac{1}{21} \,. \\ \nn \\
	P(W',W,W) & = \frac{5}{9} \times \frac{4}{8} \times \frac{3}{7} \nn \\
              & = \frac{5}{42} \,. \\ \nn \\
	P(W,W',W) & = \frac{4}{9} \times \frac{5}{8} \times \frac{3}{7} \nn \\
			  & = \frac{5}{42} \,. \\ \nn \\
	P(W',W',W)& = \frac{5}{9} \times \frac{4}{8} \times \frac{4}{7} \nn \\
			  & = \frac{10}{63} \,. \\ \nn \\
	P(\text{last marble is white}) & = \frac{1}{21} + \frac{5}{42} + \frac{5}{42} + \frac{10}{63} \nn \\
	                               & = \frac{4}{9} \,.
\end{align}

\end{subsubquestions}





\end{subquestions}