%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 20XX Q1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{enumerate}[label = \bfseries (\alph*)]
		% 1 (a)
		\item
		\begin{enumerate}[label = \bfseries (\roman*)]
			% 1 (a) (i)
			\item  A, D and E can be obtained through some quantifiable measurable process.

			% 1 (a) (ii)
			\item B and C are descriptive, subjective or difficult to measure.

			% 1 (a) (iii)
			\item A, E can all be counted.

			% 1 (a) (iv)
			\item  D can take any value within a range.

			% 1 (a) (v)
			\item B and C because it is qualitative data


		\end{enumerate}

		% 1 (b)
		\item A sample of $20$ may be selected using different sampling methods.

		\begin{enumerate}[label = \bfseries (\roman*)]
			% 1 (b) (i)
			\item We can identify the following
			\begin{itemize}
				\item $G$: Simple random
			\end{itemize}

			% 1 (b) (ii)
			\item The question fails to inform us of the population size. Assuming that the population size mentioned in a subsection is $300$, we know that $n$ must divide the $300$ cans in $20$ sections, so
			\begin{eqnarray}
			n &=& \frac{300}{20}\\
			&=& 15\
			\end{eqnarray}

			% 1 (b) (iii)
			\item We need to keep the ratio of blue in the sample representative of the ratio of blue in the entire population. Then, the number of blue in the sample, $n_b$, must satisfy the following equation:
			\begin{eqnarray}
				\frac{120}{300}&=& \frac{n_b}{20} \\
				\Rightarrow n_b &=& 8 \
			\end{eqnarray}

			% 1 (b) (iv)
			\item \begin{enumerate}[label = (\arabic*)]
				\item Stratified sampling is more representative of the entire population. Simple random sampling sometimes leads to over or under representation of a stratum

				\item In stratified sampling, every member within a strata has an equal chance of selection. In simple random sampling, every member is the population has an equal chance of selection
			\end{enumerate}

		\end{enumerate}

		% 1 (c)
		\item From see that both quantities are numerical measures. However, the parameter is calculated from the population whereas the statistic is calculated from the sample data.



	\end{enumerate}